---
title: "STANLEY_Assignment_8"
author: "Stanley"
date: "April 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(modelr)
library(tidyverse)
library(aod)

```

### I wanted to see if your undergrad school rank matters in grad school admisions.

####to do this rank needed to be turned into a factor so it is treated catogoricaly and then made a model.
```{r echo=TRUE}
df = read.csv("./GradSchool_Admissions.csv")
class(df$rank)
df$rank = as.factor(df$rank)

mod1 = glm(admit ~ gpa+gre+rank, data = df, family = "binomial")
summary(mod1) 
confint(mod1) #confidence intervals
confint.default(mod1) #confidence intrervals

```

#### this output shows us the GRE affects the admissions just a little bit with a .002 increase. GPA is a better factor with an increase in 0.804. However, rank is different where each deacreasing rank decreases your possibilies of getting in. 

#### next we need to see if these differences are statisicaly significant with a wald.test

```{r echo=TRUE}
wald.test(b = coef(mod1), Sigma = vcov(mod1), Terms = 4:6)


```

#### from this we can see the school rank is statistically significant. but now I want to see if the difference between rank 2 and 3 as well as 3 and 4.

```{r echo=TRUE}
l = cbind(0,0,0,1,-1,0)
wald.test(b = coef(mod1), Sigma = vcov(mod1), L=l)

k = cbind(0,0,0,0,1,-1)
wald.test(b = coef(mod1), Sigma = vcov(mod1), L=k)

```

#### from this we can see that the between the difference between 2 and 3 is statistically significant while between 3 and 4 it is not.

#### finaly I want to the prediced likelihood for getting in based on school rank with an average GPA and an average GRE score
```{r echo=TRUE}
new.df1 = with(df, data.frame(gre = mean(gre), gpa = mean(gpa), rank = factor(1:4)))
new.df1$rankP <- predict(mod1, newdata = new.df1, type = "response")
new.df1


```

##Conclusion 
#### based on the results from the moddle your school rank matters most if you go to a top tier undergraduate school and the differences get smaller to the point where its insignificant the between lower tiers. 

